Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd

model_1 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

##Model 6: 
StateColor + per_capita_income + (StateColor | State)
```{r, warning = FALSE, cache=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_6 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + per_capita_income + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 3, iter = 3000*2
)
```

```{r}
head(data.frame(summary(model_6)),-2)
```

@@

##Model 8:

StateColor + totalTestResults + (StateColor | State)

model_8 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```
```{r}
head(data.frame(summary(model_8)),-2)
```

@@

model_9 <- stan_glmer(
  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 3000*2
)
```

@@

>>>>

model_5 <- stan_glmer(
  ChinaVirusInterest ~ StateColor + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

```{r}
head(data.frame(summary(model_5)),-2)
```

Checks:

```{r}
# Trace plots
#mcmc_trace(model_5)

# Density plots
#mcmc_dens_overlay(model_5)
```

```{r}
# y = original sample, yrep = MCMC simulation
set.seed(454)
pp_check(model_5, nreps = 50)
```

```{r}
# Store the chains
model_5_df <- as.array(model_5) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_5_df <- model_5_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

ggplot(model_5_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

```{r}
#set.seed(454)
#my_data <- data.frame(StateColor = "red", State = "FL")

# Simulate a set of predictions for each case in newdata
#my_prediction <- posterior_predict(
 # model_5, 
  #newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) + 
 # geom_density()

#summary(my_prediction)
```

@@

```{r}
# y = original sample, yrep = MCMC simulation
set.seed(454)
pp_check(model_7, nreps = 50)
```

```{r}
# Store the chains
model_7_df <- as.array(model_7) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_7_df <- model_7_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

ggplot(model_7_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

```{r}
# set.seed(454)
# my_data <- data.frame(StateColor = "blue", State = "IL", percent_asian = .12)
# 
# # Simulate a set of predictions for each case in newdata
# my_prediction <- posterior_predict(
#   model_7,
#   newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) +
 # geom_density()

#summary(my_prediction)
```

@@

model_9 <- stan_glmer(
  ChinaVirusInterest ~ StateColor +percent_asian + totalTestResults + (StateColor | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 1000*2
)
```

@@

```{r}
# y = original sample, yrep = MCMC simulation
set.seed(454)
pp_check(model_9, nreps = 50)
```

```{r}
# Store the chains
model_9_df <- as.array(model_9) %>% 
  melt %>% 
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_9_df <- model_9_df %>% 
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

ggplot(model_9_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

```{r}
#set.seed(454)
#my_data <- data.frame(StateColor = "red", State = "FL")

# Simulate a set of predictions for each case in newdata
#my_prediction <- posterior_predict(
 # model_5, 
  #newdata = my_data)

#my_prediction <- data.frame(y_new = my_prediction[,1])

#ggplot(my_prediction, aes(x = y_new)) + 
 # geom_density()

#summary(my_prediction)
```
